\chapter*{\textsc{Acknowledgements}}

\vspace{-0.8cm}

This thesis is the culmination of six years of my life and has only been possible thanks to the amazing support I have had along the way. 

Firstly and most importantly to my partner, Gabriella, without whose support I would not have made it to the conclusion. Thank you for your encouragement, your support, and for believing in me. %You are my rock.

I would like to thank my supervisors Daniel Huber, Charles Kuehn, Dennis Stello and last but certainly not least Tim Bedding for their ideas, support, and knowledge without which this project would not have been possible. Thanks also to the Asteroseismology group in general for tips, pointers and general discussions about everything from coding to theory. 

I have been incredibly lucky to have an amazing mentor for the past few years of my PhD whose support and guidance helped me through the tough times and kept me on track to actually completing this thesis. Jesse van de Sande, your support helped make this thesis a reality so thank you.

To all of my uni friends who have kept me sane throughout this PhD with conversations, coffee, offers of support and (after work!) beers you are too many to name but thank you. In particular I would like to thank Simon and Stephanie Murphy, Joe Callingham, Ben Pope, Jane Kaczmarek, Rebecca McElroy, Hamish Clark, Beau Bellamy and Dan Hey. 

To my friends who have been there with me through the good times and the harder times, you are amazing. In particular thanks go to Joshua Stretton and Cameron Austin

Mum and Dad, you have always pushed and supported me to strive and be the best I could be. Thank you for all your support, love and encouragement throughout my life. (Even if you did run away for the last 2 years ;P )

% The moderate wonder that is completing my PhD is in no small part due to the wonderful people in my life. 

% Firstly I would like to thank my supervisors. 
% Scott Croom, I have learnt so much from you. Thank you for your guidance, patience, and time. Michael Pracy, thank you for answering infinite stupid questions in my early graduate career for and teaching me how to be sceptical. When additional supervision was required, the support of the SAMI team at SIfA was invaluable to me. In particular I would like to thank Jesse van de Sande, Julia Bryant, and Nic Scott. Thank you for helping every time I knocked on your door. The Radio Galaxy group, in particular Dick Hunstead and Elaine Sadler, thank for your the lively discussions and interesting insights into my work (and the Tim-Tams). 

% I have been incredibly privileged to have the opportunity to work with the members of the CARS collaboration throughout my PhD. You are all incredibly kind and talented scientists, and working with MUSE data is every optical astronomer's dream. Particular thanks are owed to Bernd Husemann who has become a pseudo-supervisor to me - thank you for always being willing to help and for the occasional reality check. 

% To the cult that is Serenity 335A (my evil twin Jessica, Adam, Hamish, and Joe); I could not have picked more entertaining or distracting officemates. The constant antics made the inordinate amount of time we spent in that office not only bearable, but enjoyable. I'm not sure the phrase `a burden shared is a burdened halved' applies here, but it certainly helped to suffer in such good company. Thank you for being there for me whether I was Chad or Chadwick with tea, whisky, or a shoulder to cry on. I would also like to thank the senior PhD students and postdocs, in particular Jane, Shari, Sarah, and Liz. Firstly for being living proof that a PhD does end, and secondly for always believing I would make it. 

% To my fabulous friends, thank you for reminding me that there is a world outside academia. Our constant calendar of events have kept me (relatively) sane in these last few months. Though I may be sashay-ing away, my heart will always be in the Inner West. 

% Finally, my greatest thanks are owed to my parents who supported and fed me throughout much of my university career. Thank you for always being there when I needed you with wine, delicious food, and a safe place to run away to. 

